\chapter{Introduction}

\section{Motivation}

Deep learning a part of machine learning with the marketing reach of artificial intelligence is more prensent than ever.
The increase of computaional power enabled the integration of deep learning concepts in real-world scenarios.
Training of large datasets for supervised learning models leads to a lot of problem solvers and automation in business and private areas of society.
The technology influences a large amount of people every day with rising tendency.
Well-known uses are algorithms for search, personalized adds, voice assistants, autonomous vehicles, transportation and network security.
\hfill \break
Scientist with technical knowledge integrade the concepts of deep learning into nearly every industry and branch.
Great examples for current real-world easements are in Healthcare, Marketing and agriculture:

IBM develops software that supports diagnosing, treating and predicting outcomes in medical situations.
Their deep learning algorithms have the ability to read and filter unstructured data, find similarities between patients and finding information in medical literature that helps to discover new insights.
Doctors benefit from personalized patient treatment plans and better analysis by the monitoring of patients. Researchers can discover new insights in drug development.
Currently the IBM Watson Healthcare software helps more than 230 healthcare organizations worldwide with more than 15,000 clients and partners. Their cognitive offerings have impacted care or social services for more than 295,000 people.
\cite{ibm-watson-healthcare, ibm-watson-facts}

Airbnb, a online marketplace for renting homes uses deep neural networks for categorising its listing photos.
Their customers decision is influenced by a diverse set of images.
Many home providers label their images wrong and have not enough variety in their collection.
Moreover their total amount of photos is nearly half a billion images.
Deep learning helps them identifying the picture and presenting them on the site properly.
Moreover they can detect certain objects in the images, which enable custom filters and searches for objects.
\cite{airbnb-ic-video, airbnb-ic-blog}

Connecterra developed an intelligent dairy farmer assistant.
They discovered that the production of milk is based on the animal’s health.
With an animal observation and machine learning they are able to diagnose problems early and provide health recommandations to the farmers.
\cite{tensorflow-stories, connecterra-video, connecterra-web}

The latest outstanding milestone in research: AI had beaten two of the worls's best StarCraft 2 players.
StarCraft, a Real-Time Strategy (RTS) game was called the "grand challenge" for AI because of the game complexity.
To win in this game the algorithm needs to develop continually new frontiers of strategic knowledge.
Moreover there are crucial information hidden that must be actively discovered in real-time. On top of it there are a lot of units and buildings that must be controlled at once.
By winning against two of the world's best players without any game restrictions they were able to master the "grand challenge" for AI research.
It was achieved using a deep neural network that is trained by supervised learning and reinforcement learning.
The developed techniques could be useful in other problems which involve predictions over very long sequences such as weather predition \& climate modeling.
\cite{alphastar}

These use-cases show great solutions for real-world problems solved with deep learning approaches.
However, current deep learning solutions are facing two major challenges:

One task is the duty for society is to think about ethics.
Through all new achievements with deep learning there are manny people concerned about issues in AI Governance.
Only a few indirect limitations and laws ensure the proper handling.
First steps towards a solution to ethical questions are high level negotiations and branch or use-case specific regulations. \cite[page 3]{google-ai-governance}
Additional first steps are made by the economy.
Some companies like the German Telekom \cite{telekom-ai-guidelines} or Google \cite{google-ai-principles} regulate their actions based on own general principles.
% TODO deeper, what are the principles?
Moreover they participate in giving deeper insights to the technology and proposing safety considerations.
\cite{google-ai-governance}
% TODO deeper, what are some topic insights
The responsibility of a principle development lies in the hand of society.

The second obstacle is the ongoing improvement in machine learning: 
\hfill \break
Deep learning techniques have been proven shining with a large number of labeled datasets.
With new attention to unsupervised and reinforement learning which are aiming to solve complex tasks without explicit knowledge improves the effort of creating datasets for training models.
However, most deep learning techniques are solving specific, isolated tasks which are not able to learn new tasks with a given model.
\cite{continual-ai-blog}
Many real-world scenarios require the ability of multi-task learning.
Multi-task learning menas that deep neural networks are able to learn multiple consecutive tasks without forgetting previous tasks.
This challenge results in the paradigm of "continual learning".
Other common designations are "incremental learning", "continuous learning" or "lifelong learning".
The oldest term is "lifelong learning" and was used in areas outside of deep learning.
\cite{continual-ai-blog}
This is why there were the introduction of modern terms like "continuous" or "continual", which are targeting specifically deep learning algorithms.
\cite{continual-ai-blog}
The Oxford Dictionary says that "continuous" is five times more prominent than "continual" and refers to "no interruption". "Continual" on the other hand includes the meaning of "inbetween intervals" or "happening frequently".
\cite{oxford-continual-continuous}
The meaning of "Continual" is a closer definition to this article and will be used together with the term of "incremental", which is a more technical term for the domain.
\hfill \break

% irgendwie die beiden unteren punte einbauen und auf general intelligence zu sprechen zu kommen
% what are more achievemnts:
% scale
% machine intelligence

% closer: that it is as important as reinforcement learning for a machine general intelligence

These ideas of continuously and adaptively learning about new features would enale an autonomous incremental development and the ability of learning more complex skills and knowledge.
\cite{continual-ai-blog}

One major step towards an artificial general intelligence or machine intelligence is the removing of the barrier which is called "catastrophic forgetting".
% Um dies zu erreichen muss die techbologie zuerst die große Hürde des catastrophic forgetting beseitigen.

% touch the big problem big problem: catastrophic forgetting
% first solution tries with algorithms

\section{Related Work}

% great use-case that touches both challenges


\subsection*{Better Weight Consolidation}

This paper proposes an improvement of the Elastic Weiht Consolidation. They specifically address the diagonal assumption made by the EWC algorithm.

https://arxiv.org/pdf/1802.02950.pdf


\section{Project Introduction}

… % TODO
% the first dolution tries use all one fisher matrix
% calculation takes a lot of time
% idea of optimizing the algorithms with a adjustment of the matrix

% the goal to optimize these algorithms that they may be used in real-world scenarios